Station summary

### 2023-02-16 reports/02_stations.qmd
Fix index.md
add zooplankton maps

---
title: "Station summary"
format:
  html:
    code-fold: true
editor: visual
output-dir: "docs"
---

@@

## Zooplankton community/physics maps

```{r}
#| label: zoop_physics_maps

zoop_physics_vars <- c("Winter Cluster factor",
                       "Net.ice.type",
                       "Net.ice.percent",
                       "zuml_m",
                       "avg.Dens.Diff",
                       "avg.salinity",
                       "avg.temp",
                       "Water.Zone",
                       "Integ.chla.zuml",
                       "Integ.phae.zuml",
                       "Integ.chla.100m",
                       "Integ.phae.100m")

@@

walk(zoop_physics_vars, compose(print, station_map))

@@

>>>>

---
title: "Station summary"
format:
  html:
    code-fold: true
    toc: true
editor: visual
output-dir: "docs"
---

@@

## Zooplankton maps

```{r}
#| label: station_map_fn

@@

@@

```{r}
#| label: zoop_maps

zoop_vars <- c("Winter Cluster factor",
               "NMDS_x",
               "NMDS_y",
               "NMDS_z",
               "Amphipoda_Primno_N.A",
               "Amphipoda_Themisto_N.A",
               "Chaetognatha_N.A",
               "Copepoda_Cacutus_N.A",
               "Copepoda_Cprop_N.A",
               "Copepoda_Heterorhabdus_N.A",
               "Copepoda_Metridia_N.A",
               "Copepoda_Paraeuchaeta_N.A",
               "Copepoda_Pleuromama_N.A",
               "Copepoda_Rhincalanus_N.A",
               "Euphausiidae_Ecrystall_Adult",
               "Euphausiidae_Efrigida_Adult",
               "Euphausiidae_Efrigida_Larvae",
               "Euphausiidae_Esuperba_Adult",
               "Euphausiidae_Etricantha_Adult",
               "Euphausiidae_Tmac_Adult",
               "Euphausiidae_Tmac_Larvae",
               "Gastropoda_Clione_N.A",
               "Gastropoda_Limacina_N.A",
               "Ostracoda_N.A",
               "Radiolaria_N.A",
               "Siphonophora_N.A",
               "Tunicata_Salpa_N.A",
               "Euphausiidae_Esuperba_F_Tot",
               "Pisces_Paralepididae_NotolepisSpp_Larvae_Tot",
               "Pisces_Myctophidae_Adult_Tot",
               "Pisces_Myctophidae_Larvae_Tot",
               "Pisces_Other_Larvae_Tot",
               "Pisces_Chaenichthyidae_Larvae_Tot",
               "Pisces_Nototheniidae_Larvae_Tot")

walk(zoop_vars, compose(print, station_map))

## Physics maps

```{r}
#| label: physics_maps

physics_vars <- c("Net.ice.type",
                  "Net.ice.percent",
                  "zuml_m",
                  "avg.Dens.Diff",
                  "avg.salinity",
                  "avg.temp",
                  "Water.Zone",
                  "Integ.chla.zuml",
                  "Integ.phae.zuml",
                  "Integ.chla.100m",
                  "Integ.phae.100m")

walk(physics_vars, compose(print, station_map))
